---
title: "Manipulations"
author: "Brett Graham"
date: "3/23/2018"
output: html_document
---
Simplifying & joining raw datas
```{r}
# Creating list that contains the IDs for census variables (Unemployed in labor force, poverty status, population Total, pop In Labor Force)
census_variables <- c("C18120_006E", "B17021_001E", "B01003_001E", "B23025_002E")

# Creating table using tidycensus for each zipcode
tidycensusPopulationInfo <- 
  get_acs(geography = "zip code tabulation area", variables = census_variables) 
```
```{r}
# Tidying up the data to include unemployment rate, poverty rate as well as change column names to be more descriptive
censusInfoForZipCode <- tidycensusPopulationInfo %>%
  select(GEOID, variable, estimate) %>%
  spread(key= "variable", value = "estimate") %>%
  rename(unemployedInLaborForce = C18120_006, 
         povertyStatus = B17021_001, 
         populationTotal = B01003_001,
         popInLaborForce = B23025_002) %>% 
  mutate(unemploymentRate = unemployedInLaborForce/popInLaborForce,
         povertyRate = povertyStatus/populationTotal)
```

```{r}
# cleaning zipCode
zipCodeDataClean <- zipCodeData %>%
  select(Zipcode, City, State, Lat, Long)

# merging zipcode and city data with zipCodeInfo
newZipWithCityInfo <- censusInfoForZipCode %>%
  left_join(zipCodeDataClean, by = c("GEOID" = "Zipcode"))

newZipWithCityInfo <-newZipWithCityInfo[,c(8,9,1,2:7,10:11)]
newZipWithCityInfo <-newZipWithCityInfo[newZipWithCityInfo$State != "PR", ]
```

```{r}
cityUnemployment <- newZipWithCityInfo %>%
  group_by(City,State) %>%
  summarize(populationTotal=sum(populationTotal),
         popInLaborForce=sum(popInLaborForce),
         unemployedPop = sum(unemployedInLaborForce),
         unemploymentRate = unemployedPop/popInLaborForce,
         lat = mean(Lat),
         long = mean(Long))
```

```{r}
stateUnemployment <-newZipWithCityInfo %>%
  group_by(State) %>%
  summarize(populationTotal=sum(populationTotal),
         popInLaborForce=sum(popInLaborForce),
         unemployedPop = sum(unemployedInLaborForce),
         unemploymentRate = unemployedPop/popInLaborForce,
         lat = mean(Lat),
         long = mean(Long))
```

Modifying Indeed Data

```{r}
#Simplifies the indeed into the job, state, and number of clicks/ applications  
simplifiedIndeed <- indeedData %>%
  select(c("jobHash","admin1","city","clicks","applies"))
```

```{r}
#Summarizes by job postings
sumJobs <- simplifiedIndeed %>% 
  group_by(jobHash, admin1,city)%>%
  summarize(totalClicks = sum(clicks),totalApplies = sum(applies),days = n())
```

TODO
```{r}
#summarizes state click info
sumCity <-sumJobs %>%
  group_by(admin1,city) %>%
  summarise(cityClicks = sum(totalClicks),cityApplies = sum(totalApplies),jobPostings = n()) %>%
  mutate(appliesPerClick = cityApplies/cityClicks, clicksPerPosting = cityClicks/jobPostings)%>%
  mutate(city = toupper(city))
  
  
```

```{r}
#summarizes state click info
sumState <-sumJobs %>%
  group_by(admin1) %>%
  summarise(stateClicks = sum(totalClicks),stateApplies = sum(totalApplies),jobPostings = n()) %>%
  mutate(appliesPerClick = stateApplies/stateClicks, clicksPerPosting = stateClicks/jobPostings)
  
  
```

```{r}
indeedCityRaw <- sumCity %>%
  inner_join(cityUnemployment,by = c("city"="City"))%>%
  subset(select=c(-State)) %>%
  rename(State=admin1)
  
```

```{r}
#Merge State Indeed data with census data
indeedStateRaw <- sumState %>%
  inner_join(stateUnemployment,by = c("admin1"="State")) %>%
  rename(State = admin1)
```


Data Manipulations
```{r}
indeedState <- indeedState %>%
  mutate(jobsPerUnemployed = jobPostings/unemployedPop)
```

```{r}
indeedCity <- indeedCityRaw %>%
  mutate(jobsPerUnemployed = jobPostings/unemployedPop)




```













































=======
# Modifying internet access by city data to extrapolate to 2016
internetAccess2016 <- internetAccess %>%
  mutate(expPercInternetUse = (1-((1- (percentHouseholdsWithIntAcc/100))/2))) %>%
  separate(`city,State`, into = c("City", "State"), sep = ", ") %>%
  mutate(City = toupper(City), percentHouseholdsWithIntAcc = percentHouseholdsWithIntAcc/100)

intAccEnhanced <- internetAccess2016 %>%
  left_join(states, by = c("State"="State")) %>%
  mutate(State = Abbreviation) %>%
  select(-Abbreviation)
```
